### 2013-07-18 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
editing nonlinear chapter

\begin{itemize}
\item MCSA can be effectively parallelized using domain decomposition
\item The leakage fraction of stochastic histories from a parallel
  subdomain can be quantified analytically using algebraic quantities
\item The multiple-set overlapping-domain (MSOD) parallel algorithm
  for particle transport has been adapted to parallelize MCSA
\item MCSA parallelized with MSOD was verified to produce the same
  results for solutions to the neutron diffusion equation as
  production Krylov methods
\item Strong scaling studies were performed with up to 65,536 cores
  and weak scaling studies were performed with up to 131,072 cores on
  the Titan Cray XK7 leadership class machine at Oak Ridge National
  Laboratory
\item MCSA scales favorably compared to production Krylov methods for
  both strong and weak scaling cases
\item Overlap in small quantities determined analytically by random
  walk length can provide parallel efficiency boosts of a few percent
  in strong scaling cases but is ineffective in weak scaling cases
\item Multiple sets will never boost parallel efficienicies in both
  weak and strong scaling cases due to additional communication
  overhead from added reduction operations
\item Multiple sets offers a means to reduce time to solution by
  solving a multiple copies of the original problem and combining the
  solutions using superposition
\item MCSA is most efficient used in parallel as a stochastic
  realization of an additive Schwarz method
\item With future optimization, large scale reactor analyses in which
  the transport operator is fully formed (e.g. the $SP_N$ equations)
  could experience improved time to solution on leadership-class
  machines with MCSA given the improved scaling performance
\end{itemize}

>>>>

\begin{itemize}
\item MCSA can be effectively parallelized using domain decomposition
\item The leakage fraction of stochastic histories from a parallel
  subdomain can be quantified analytically using algebraic quantities
\item The multiple-set overlapping-domain (MSOD) parallel algorithm
  for particle transport has been adapted to parallelize MCSA
\item MCSA parallelized with MSOD was verified to produce the same
  results for solutions to the neutron diffusion equation as
  production Krylov methods
\item Strong scaling studies were performed with up to 65,536 cores
  and weak scaling studies were performed with up to 131,072 cores on
  the Titan Cray XK7 leadership class machine at Oak Ridge National
  Laboratory
\item MCSA scales favorably compared to production Krylov methods for
  both strong and weak scaling cases
\item Overlap in small quantities determined analytically by random
  walk length can provide parallel efficiency boosts of a few percent
  in strong scaling cases but is ineffective in weak scaling cases
\item Multiple sets will never boost parallel efficienicies in both
  weak and strong scaling cases due to additional communication
  overhead from added reduction operations
\item Multiple sets offers a means to reduce time to solution by
  solving multiple copies of the original problem and combining the
  solutions using superposition
\item MCSA is most efficiently used in parallel as a stochastic
  realization of an additive Schwarz method
\item With future optimization, large scale reactor analyses in which
  the transport operator is fully formed (e.g. the $SP_N$ equations)
  could experience improved time to solution on leadership-class
  machines with MCSA given the improved scaling performance
\end{itemize}

### 2013-07-18 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
editing nonlinear chapter

\begin{itemize}
\item MCSA can be used to solve the asymmetric system generated by the
  multigroup $SP_N$ equations
\item MCSA has been incorporated into the Exnihilo neutronics
  production code base developed at Oak Ridge National Laboratory
\item Simple Jacobi-based preconditioning reduces the spectral radius
  of the $SP_N$ system below unity, however, this is not sufficient
  for MCSA convergence
\item As the spectral radius approaches unity, MCSA was demonstrated
  to break down with more stochastic histories required for
  convergence and more CPU time required per history
\item Advanced algebraic preconditioning strategies were applied to
  the $SP_N$ equations to obtain convergence with ILUT chosen for
  subsequent investigations
\item The reduced domain approximation was required to mitigate the
  memory and performance constraints of the explicit preconditioning
  strategy although both remain significant obstacles
\item MCSA relaxation parameters were developed an observed to enhance
  the time to solution for the fuel assembly problem
\item MCSA was verified to produce the same flux distribution and
  k-eigenvalue for the fuel assembly as production Krylov methods
\item MCSA was observed to converge in fewer iterations per eigenvalue
  iteration than GMRES for the fuel assembly problem and more then
  Bi-CGStab
\item The explicit preconditioning strategy creates MCSA runtimes
  $O(100)$ larger than the production Krylov methods for the fuel
  assembly problem
\end{itemize}

>>>>

\begin{itemize}
\item MCSA can be used to solve the asymmetric system generated by the
  multigroup $SP_N$ equations
\item MCSA has been incorporated into the Exnihilo neutronics
  production code base developed at Oak Ridge National Laboratory
\item Simple Jacobi-based preconditioning reduces the spectral radius
  of the $SP_N$ system below unity, however, this is not sufficient
  for MCSA convergence
\item As the spectral radius approaches unity, MCSA was demonstrated
  to break down with more stochastic histories required for
  convergence and more CPU time required per history
\item Light water reactor problems are difficult to solve with MCSA as
  they have large spectral radii due to the neutron scattering in the
  moderator
\item Advanced algebraic preconditioning strategies were applied to
  the $SP_N$ equations to obtain convergence with ILUT chosen for
  subsequent investigations
\item The reduced domain approximation was required to mitigate the
  memory and performance constraints of the explicit preconditioning
  strategy although both remain significant obstacles
\item MCSA relaxation parameters were developed and observed to
  enhance the time to solution for the fuel assembly criticality
  problem
\item MCSA was verified to produce the same flux distribution and
  k-eigenvalue for the fuel assembly as production Krylov methods
\item MCSA was observed to converge in fewer iterations per eigenvalue
  iteration than GMRES for the fuel assembly criticality problem and
  more then Bi-CGStab
\item The explicit preconditioning strategy creates MCSA runtimes
  $O(100)$ larger than the production Krylov methods for the fuel
  assembly criticality problem
\end{itemize}
